Teaching a Class to Grade Itself using Game Theory

### 2013-09-05 Primes Write up.tex
Revised Paper

\documentclass[12pt, Helvetica]{article}   	
\title{Primes Paper}
\author{Nick Kaashoek and William Wu}
\usepackage[margin=1in]{geometry}
\usepackage{parskip}
\setlength{\parindent}{15pt}
\begin{document}
\maketitle
\section{Introduction}
Over the past few years, there has been a tremendous increase in the popularity of MOOCs (Massive Open Online Courses), as well the importance of MOOCs to education as a whole. Popular MOOC systems such as Corsera or EdX are well funded, which explains their rapid growth: EdX is funded by 60 million dollars\cite{canmoocsreducecc}. However, the MOOC's main importance comes from it's scalability. Moocs are able to educate massive numbers of students from anywhere in the world\cite{makingsenseofmoocs}: In Coursera alone, there are 1.7 million students\cite{swotanalysisofmoocs}. The sheer number of students leads to high student-professor ratios that can reach 150,000:1 in some courses.

High student-professor ratios lead to problems for professors. Professors are unable to grade hundreds of thousands of sumbissions from a single homework assignment: a major problem. Currently, there are two ways to remedy the problem: automated grading and peer grading. Automated grading relies on machines to grade assignments. However, machines can only check certain types of answers, severly limiting the depth of the questions asked\cite{rightandwrongmoocs}. On the other hand, peer grading can grade any type of question, but a system utilizing it could easily be "hacked" by the students \cite{makingsenseofmoocs}. Although both of these systems are interesting concepts, they are unpolished and inefficient in practice.

The problem that we have located is important to solve. Without a solid solution, MOOCs cannot provide efficient feedback for their students, rendering them unable to effectively evaluate their knowledge. Because this limits their learning abilities, it is imperitive to create an efficient system that enables students to learn efficiently and grow. This is our goal.

There have been many attempts at solving such an important problem. However, we hope to introduce what all previous attempts lack: a rigourous mathematical proof and analysis of the system. With our system, we hope to introduce a set of criteria that the system must pass, and then analyze it mathematically to prove the efficiency of our solutions. Introducing this to the problem will help to create a concrete system of grading that will consistently and universally produce positive results, both in terms of efficiency, and fairness for the students.

To efficiently prove a mathematical system such as we proposed, we need to lay out some tools first, chief among them being mechanism design and game theory. Without the correct tools, it is impossible to do the neccesary mathematical analysis on human behavior in these systems, so we turn to game theory. Game theory allows us to create a system of rules that have to be followed by everyone in the system. By manipulating these rules, we are able to change the behavior of everyone in the system. By adding basic assumptions about human nature, we are able to predict what will happen with a specific set of rules, and prove it; this will be how we prove and create our mechanism.

Our end goal with this project is to develop a mathematically provable and efficient mechanism to incentivize selfish people to accurately grade the assignments of others. By assuming that all the students in the system care about themselves, we assume that they are selfish. With this in mind, the problem becomes an issue of incentivization; how do we make these selfish people care about others? As such, our goal is to find the perfect incentive for these people. If we are succesful, this will make them grade the papers of others efficienly because they care, and fairly because they are human: this strikes the perfect balance between the two current solutions.

Mathematically provable systems like the one that we are trying to create always lead to good results. For example...

Some people might think that this is a rather simple problem to solve, and could come up with a variety of simple solutions that appear to be correct. Incentivizing people often seems simple at first; for example, why not just say "here, take this paper and grade it. I'll give you bonus points if you do it." Obviously, this will just return garbage because the students will just take the points and not care about the grading. The next step would be to implement some kind of simple checking: "here, you two students, take this paper and grade it. If you match, I'll give you bonus points." This case may seem like it works if the students are isolated, but smart students will just give the paper 100, not grade, match and get the points. Clearly, simple solutions aren't really that effective

As demonstrated by the above examples, this problem's complexity lies in the complex behavior of selfish human beings; as such, there is no simple way to solve it. Because human nature dictates that people will do whatever is in their best interests and will always try to outsmart the system, it quickly becomes apparent that a strict set of rules and assumptions is neccesary to dictate thier behavior. The rules, however, can never be to simple, because they need to anticipate every possible way the players (students) will attempt to outsmart them. This means that although we will try to create a relatively simple solution, it can never be to straightforward.

The complexity of human nature is what makes the problem interesting; this combined with its relevance makes it an interesting research oppurtunity. Although there may not be a simple and beautiful solution to this problem, our use of game theory to predict human nature provides tremendous grounds for interesting research. Not only does predicting human nature make this interesting, but the problem's relevance to modern times also means that this is a neccesary problem to solve, giving us good basis to design our solution on.

@@

@@

\section{The First Model}
This model is quite unrealistic, but not by such a degree that it is unimaginable. We were, however, able to create a perfect solution if the problem took place in this situation.
\subsection{The Mechanism}
In our model, we have the professor grade one paper, called \emph{X}. The professor then distributes all the student's papers randomly among the students, while making sure that no student receives his or her own paper. Every student is also given a copy of \emph{X}.

The professor then tells the students that "Out of the two papers you were given, one of them has been graded by me, and the other hasn't. If you fail to give the correct grade for the one I graded, then you will receive a 0." The students then go about their business grading the papers, and individually report the grades they gave out to the professor. Then, just like the professor promised, if the graders graded the pre-graded, or \emph{calibrated} paper incorrectly, then that grader gets a 0 on the assignment. If they graded correctly, the get the maximum of {some minimum value, the assigned grade}.
\subsection{Why it works}
G is the maximum of {some minimum value, the assigned grade}.

@@

This means that if $H(G) - 2 > H(0)$, then student will grade both papers. So, for the professor to guarantee that the students use effort and obtain the correct grades, he or she would choose a minimum value such that $H(G) > H(0) + 2$.
\subsection{The result}
The teacher expends one unit of effort, and the students each spend 2, as long as the teacher set the minimum value high enough.
Everything above $H^{-1}(2)$ will be graded correctly, while everything below it will receive a score of $H^{-1}(2)$.
This means that the maximum deviation is $H^{-1}(2)$, because this is the score that might be given to someone who deserves a 0. Expressed in happiness units, we get a value of 2.
The means that the value of the objective function in this case is 4, a very low value, which shows how effective this solution is.
\section{The Next Step}
We now have a model that works very well in an unrealistic scenario, so we decided that this solution was fine, and moved on to a new model. The goal for this models was to make it more realistic while still making it simple to understand, and have a simply solution that would be easy for students to understand.

The major change we made in this model was one to assumption number 11. We changed it to:

\emph{All students are able to communicate with each other}

This provides a very different scenario than our original model, because now students will be able to figure out which papers are calibrated. However, we still wanted to try and generalize our previous solution and apply it to the new model, so we came up with the following scheme.
\subsection{The New Mechanism}
Our first attempt to apply a solution to this model was a near carbon copy of the previous scheme.
We arrange the class in a virtual circle, where every student grades the papers of the \emph{k} students to the right of them. The proffesor also grades every \emph{kth} paper starting from some random point in the circle. If a student misgrades the calibrated paper, they get a 0, otherwise they get the maximum of their objective score and the minimum value from our previous mechanism.
\subsection{Why it Works and Problems}
In this scheme, because of the overlapping papers, the students have no better way of figuring out which papers are calibrated than random guessing, even though they can all communicate with each other. As such, there are 3 options for the students.

@@

The major problem with this method is the amount of work. The professor has to grade $\frac{n}{k}$ papers, which can be massive in a class of 1000+ students. For this reason we tried to come up with a different mechanism.
\section{A better mechanism}
In our new mechanism, we went with a completely different strategy, that we wanted to work better than our previous one. It works like this:

For each assignment, a new assignment is created to evaluate the performance of the graders. Every student receives 2 papers from different people, so that each paper overlaps with one other person, and every paper is distributed twice. The student then chooses how many points to subtract, and writes a justification for each one of these points. Graders are then given a contribution score from 1 to -1. From each of the 2 assignments they grade, they get their points deducted/total points deducted-0.5. Then, if the original writers of the papers can appeal their grade if they are unhappy with it. The professor will grade the paper, and if any of the graders were wrong, they get a 0. To compute the final score, the grader's final grade on the assignment is calculated as follows: 4 points times their contribution score are added or subtracted to H(your assigned grade). (Then your grade is converted from Happiness to an actual score). 
\subsection{Why it works}
The grader's have two choices, they can either grade the papers, or not grade them.

@@

-In this case, the chance of gaining points is so low that its disregardable

@@

\subsection{The result}
Because everyone is honest, we can now analyze the score of the mechanism:

@@

Although this is not as good as our previous mechanism, it is still an improvement because there is now positive competition instead of negaitve

@@

\bibitem{test}
  Author,
  \emph{Title}.
  Source,
  Year.

>>>>

\documentclass[12pt, Arial]{article}   	
\title{Teaching a Class to Grade Itself using Game Theory}
\author{Nick Kaashoek and William Wu}
\date{\today}
\usepackage[margin=1in]{geometry}
\usepackage{parskip}
\setlength{\parindent}{15pt}
\begin{document}
\maketitle
\section{Introduction}
Over the past few years, there has been a tremendous increase in the popularity of MOOCs (Massive Open Online Courses), as well the importance of MOOCs to education as a whole. Popular MOOC systems such as Coursera or EdX are well funded, which explains their rapid growth: 60 million dollars were invested in EdX when it started~\cite{canmoocsreducecc}. However, the MOOC's main importance comes from its scalability. MOOCs are able to educate massive numbers of students from anywhere in the world~\cite{makingsenseofmoocs}: By the end of 2012, 1.7 million students had attended a course through Coursera~\cite{swotanalysisofmoocs}. The sheer number of students leads to high student-professor ratios that can reach 150,000:1 in some courses.

High student-professor ratios lead to problems for professors. Professors are simply unable to grade hundreds of thousands of submissions. Currently, two types of solutions are used to remedy the problem: automated grading and peer grading. Automated grading relies on machines to grade assignments. However, machines can only check certain types of answers (i.e. multiple choice), severely limiting the depth of the questions asked~\cite{rightandwrongmoocs}. Even though automated grading for written essays is an active area of research with much recent progress, a usable solution does not yet exist~\cite{automatedsystemssuck}. On the other hand, peer grading can grade any type of question, but a system utilizing it could easily be ``hacked'' by the students~\cite{makingsenseofmoocs}. Although both of these systems are interesting concepts, they are limiting or inaccurate in practice~\cite{howaccurateispeergrading}.

The problem of grading large numbers of submissions is important to solve. Without a solid solution, MOOCs cannot provide efficient feedback for their students, rendering them unable to effectively evaluate their knowledge. Because this limits their learning abilities, it is imperative to create an efficient system that enables students to receive feedback to learn efficiently.

There have been many attempts at solving such an important problem~\cite{autograding}~\cite{edxsoftware}. However, this work introduces what previous attempts lack: a rigorous mathematical analysis of the system using tools from game theory and mechanism design. This work sets a concrete set of constraints that a grading system must satisfy to mitigate student incentive to cheat, as well as a concrete benchmark to analyze the efficiency of various systems. Together, these create a concrete measure for evaluating peer grading systems in terms of efficiency (how much time the professor and students spend grading) and fairness for the students (how accurate their final scores are). Having this measurement model is a large contribution in itself, because it allows comparison between different systems. Although a theoretical model cannot predict exactly what will happen in practice, game theory and mechanism design have a history of generally determining mechanisms that work in practice from ones that do not. Mechanisms that do not follow game theoretic constraints may work in the short-term, but they will be exploited if possible in the long term~\cite{boycottfinal}.
%[Note from Matt and Christos: 1) mention that coming up with a model is itself a big contribution, because now we can compare the quality of two different mechanisms. 2) Mention that certainly theory is not a perfect predictor of what will happen in practice, but that game theory and mechanism design (and all the assumptions used in this work) have a history of ``calling good mechanisms good and bad mechanisms bad''. Also, solutions that do not satisfy game theoretic constraints may work for a while, but in the long run if a system can be exploited, eventually it will be. See here for an interesting example of this: http://www.insidehighered.com/news/2013/02/12/students-boycott-final-challenge-professors-grading-policy-and-get]

Game theory allows the creation of a unified system of assumptions that simulate student behavior in a class. The grading system can be viewed as a ``game'' where the set of ``rules'' are known to everyone and the ``players'' --- the students --- ``play'' the game in order to get the best possible result. Using the assumptions and rules, game theory can predict how students will behave when they ``play''. This way, mechanism efficiency and effectiveness cam be proved, allowing the evaluation of different sets of rules.

In addition to modeling grading systems, this project develops a mechanism in which students accurately grade the assignments of other students. Students are assumed to be self-interested; they care about their own grades, not the grades of their peers. With this, the problem becomes how to find the perfect incentive for students to spend time to grade assignments of others. Incentivizing students seems simple at first: let the professor give bonus points to students who grade, for example. However, this may not return anything useful because a clever student will just take the points and assign a generic grade (i.e. they will just give every assignment a 100). The next step would be to implement simple checking: e.g. have each paper be graded by two students who both receive bonus points if their grades match. This case may work if the students are isolated, but clever students will still just give all papers 100. This way, their papers will match those of other clever students, giving them points without grading. These examples show that properly incentivizing graders can be a difficult task.

As demonstrated by the above examples, the complexity of the problem lies in the complex behavior of selfish human beings. Because human nature dictates that people will do whatever is in their best interest and may try to outsmart the system, coming up with a strict set of rules to encourage the desired behavior can be quite challenging. A mechanism should be made as simple as possible, but the above examples show that a small amount of simplicity must be sacrificed to obtain a system that can't be manipulated.

This research opportunity is made interesting by the complexity of human nature as well as its necessity for practical use. This paper will cover the thought process of models leading up to the final model of grading, as well as explain the final model and its implications. All models and related calculations will be presented. Section 2 describes the mathematical definition of the problem as well as its rules and assumptions. Section 3

@@

[Note from Matt and Christos: Add some discussion about the benchmark: why do you care about workload? Why do you care about accurate grades? If you just care about workload, give everyone 100. If you just care about grades, have the professor grade everything. Need to consider both to properly model the problem.]

@@

\section{The Calibration Model}

This model is quite unrealistic, but not by such a degree that it is unimaginable. We were, however, able to create a perfect solution if the problem took place in this situation.

\subsection{Mechanism}
In our model, we have the professor grade one paper, called \emph{X}. The professor then distributes all the student's papers randomly among the students, while making sure that no student receives his or her own paper. Every student is also given a copy of \emph{X}.

The professor then tells the students that ``Out of the two papers you were given, one of them has been graded by me, and the other hasn't. If you fail to give the correct grade for the one I graded, then you will receive a 0.'' The students then go about their business grading the papers, and individually report the grades they gave out to the professor. Then, just like the professor promised, if the students graded the pre-graded, or \emph{calibrated} paper incorrectly, then that grader gets a 0 on the assignment. If they graded correctly, their assigned grade is guaranteed to be at least some minimum value.

\subsection{Why it Works}
G is the maximum of \{ some minimum value, the assigned grade \}.

@@

This means that if $H(G) - 2 > H(0)$, then student will grade both papers. So, for the professor to guarantee that the students use effort and obtain the correct grades, he or she would choose a minimum value such that $H(G) > H(0) + 2$.
\subsection{Results}
The teacher expends one unit of effort, and the students each spend 2, as long as the teacher set the minimum value high enough.
Everything above $H^{-1}(2)$ will be graded correctly, while everything below it will receive a score of $H^{-1}(2)$.
This means that the maximum deviation is $H^{-1}(2)$, because this is the score that might be given to someone who deserves a 0. Expressed in happiness units, we get a value of 2.
The means that the value of the objective function in this case is 4, a very low value, which shows how effective this solution is.

\subsection{Problems}
The goal for this model was to make it more realistic while still making it simple to understand, and have a simply solution that would be easy for students to understand. We now have a model that works very well in an unrealistic scenario, so we decided that this solution was fine, and moved on to a new model.

\section{Improved Verification Model}
The major change made in this model was one to assumption number 11. Now assumption 11 reads as follows:
\emph{All students are able to communicate with each other}

This provides a very different scenario than our original model, because now students will be able to figure out which papers are calibrated. However, we still wanted to try and generalize our previous solution and apply it to the new model, so we came up with the following scheme.

\subsection{Mechanism}
Our first attempt to apply a solution to this model was a near carbon copy of the previous scheme.
The class is arranged in a virtual circle, where every student grades the papers of the \emph{k} students to the right of them. The professor also grades every \emph{kth} paper starting from some random point in the circle. If a student mis-grades the calibrated paper, they get a 0, otherwise they get the maximum of their objective score and the minimum value from our previous mechanism.

\subsection{Why it Works}
In this scheme, because of the overlapping papers, the students have no better way of figuring out which papers are calibrated than random guessing, even though they can all communicate with each other. As such, there are 3 options for the students.

@@

\subsection{Results}
Even though the students can communicate with one another, they will have no way to determine which paper is calibrated, and are thus best off grading all the papers.

\subsection{Problems}
The major problem with this method is the amount of work. The professor has to grade $\frac{n}{k}$ papers, which can be massive in a class of 1000+ students. For this reason we tried to come up with a different mechanism.

\section{The Deduction Model}
In our new mechanism, we went with a completely different strategy, that we wanted to work better than our previous one.

\subsection{Mechanism}
For each assignment, a new assignment is created to evaluate the performance of the graders. Every student receives 2 papers from different people, so that each paper overlaps with one other person, and every paper is distributed twice. The student then chooses how many points to subtract, and writes a justification for each one of these points. Graders are then given a contribution score from 1 to -1. From each of the 2 assignments they grade, they get their points deducted / total points deducted-0.5. Then, if the original writers of the papers can appeal their grade if they are unhappy with it. The professor will grade the paper, and if any of the graders were wrong, they get a 0. To compute the final score, the grader's final grade on the assignment is calculated as follows: 4 points times their contribution score are added or subtracted to H(your assigned grade). (Then your grade is converted from Happiness to an actual score).

\subsection{Why it Works}
The grader's have two choices, they can either grade the papers, or not grade them.

@@

-In this case, the chance of gaining points is so low that it is negligible

@@

\subsection{Results}
Because everyone is honest, we can now analyze the score of the mechanism:

@@

Although this is not as good as our previous mechanism, it is still an improvement because there is now positive competition instead of negative.

@@

\bibitem{boycottfinal}
  % http://www.insidehighered.com/news/2013/02/12/students-boycott-final-challenge-professors-grading-policy-and-get
  Author,
  \emph{Title}.
  Source,
  Year.

\bibitem{autograding}
  % http://www.ecu.edu/cs-acad/fsonline/customcf/committee/tg/2013proposals/08.pdf
  Author,
  \emph{Title}.
  Source,
  Year.

\bibitem{edxsoftware}
  % http://www.bostonmagazine.com/news/blog/2013/04/04/edx-now-has-robots-to-grade-your-essays/
  Author,
  \emph{Title}.
  Source,
  Year.

\bibitem{automatedsystemssuck}
  Herrington, A., \& Moran, C. (2012). \emph{Writing to a machine is not writing at all}. In N. Elliot \& L. Perelman (Eds.), Writing assessment in the 21st century: Essays in honor of Edward M. White (pp. 219-232). New York, NY: Hampton Press.

\bibitem{howaccurateispeergrading}
  % http://educationgroup.mit.edu/HHMIEducationGroup/wp-content/uploads/2011/05/Freeman-et-al-2010.pdf
  Author,
  \emph{Title}.
  Source,
  Year.
